---
title: "Exercise1"
format: html
author: Christoph J. Bucher
---



### Playing with Quarto

This is normal Text.

```{r}
  print('Hello VSCode')

```


### Sampling
In the following code we first set a seed to make our results reproducible and then we just drew the 100 samples from a log-norm distribution using the function rlnorm.
```{r}

set.seed(69)

mu <- 5
sigma <- 0.5

samples <- rlnorm(100, meanlog = mu, sdlog = sigma)
df <- data.frame(samples)
#print(colnames(df))

```

### Histogram plotting
Now we actually want to plot our results. For this reason, we import the ggplot library, which looks great. We can see that the log norm behaves "normally" with the tailing to the right on the linear scale and the nice normal curve after applying the log scale - with the mean at the expected place.

```{r}

library("ggplot2")





# Basic histogram
linear_hist <- ggplot(df, aes(x = samples)) +
  geom_histogram(binwidth = 10) +
  geom_vline(aes(xintercept=mean(samples)),
            color="blue", linetype="dashed", linewidth=1) +
  labs(title = "Linear Scale", x = "Value", y = "Frequency")

linear_hist


# Create a log scale histogram
log_hist <- ggplot(df, aes(x = samples)) +
  geom_histogram() +
    geom_vline(aes(xintercept=mean(samples)),
            color="blue", linetype="dashed", linewidth=1) +
  labs(title = "Log Scale", x = "Values", y = "Frequency")+
  scale_x_log10()

log_hist








```

### Violin Plots

Now we are focusing on Violon Plots. The expected violin plots are as expected from the previous visualizations.


```{r}

violin <- ggplot(df, aes(x = "", y = samples)) + 
  geom_violin() + 
  labs(title = "Violon plot", y = "Value")

violin


log_violin <- ggplot(df, aes(x = "", y = samples)) + 
  geom_violin() + 
  labs(title = "log Violon plot", y = "Value")+
  scale_y_log10()
  

log_violin


```


### Inline Mean and Standard Deviation

The mean is `r round(mean(samples), digits = 3)`, with a log of `r round(log(mean(samples)), digits = 3)`.
The standard deviation is `r round(sd(samples), digits = 3)`, with a log of `r round(log(sd(samples)), digits = 3)`.
